---
title: "Analysis for final, prereg. sample of ARL-BV"
author: "Daniel P"
output: html_document
---

# Overview
This markdown contains all analyses run on the final sample of ARL-BV

# Set up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(mc.cores=12)

path_to_project_directory <- "~/projects/ARL_bv/"
path_to_arl <- "~/projects/ARL/"
path_to_s22 <- "~/projects/spring_2022_study/"

stan_model_dir<- paste0(path_to_project_directory,"code/stan_models/final_samp_mods/")
model_out_dir <- paste0(path_to_project_directory,"output/results/stan_model_fits/final_samp_fits/")

#load custom functions
source(paste0(path_to_s22,"code/functions/s22_utilities.R")) 
source(paste0(path_to_s22,"code/functions/stan_utilities.R"))
source(paste0(path_to_arl,"code/functions/arl_utilities.R")) 
source(paste0(path_to_project_directory,"code/functions/arlbv_utilities.R")) 
source(paste0(path_to_s22,"code/functions/fit_stan_model.R"))

library(tidyverse)
library(cmdstanr)
library(loo)
library(bayesplot)
library(tidybayes)
library(lmerTest)
library(sigmoid)
library(abind)
library(future)
library(doFuture)
library(foreach)
library(posterior)
```

Read in data, run through QC
```{r}
trials <- read.csv(paste0(path_to_project_directory,"analysis_data/trial_level_data_all_subs_2023-11-27_18_52_39.243708.csv"))
subs <- read.csv(paste0(path_to_project_directory,"analysis_data/sub_level_data_all_subs_2023-11-27_18_52_39.243708.csv"))

sub_hard_fail <- subs %>% filter(att_checks_passed < 5 |
                                 valrat_skipped_percent > .1 |
                                 late_percent > .2 |
                                 consecutive_late_choices > 9 |
                                 trials_completed < 144 |
                                 sd_valrat < .05 |
                                 percent_left > .8 |
                                 percent_left < .2 |
                                 percent_left_b1 < .1 |
                                 percent_left_b1 > .9 |
                                 percent_left_b2 < .1 |
                                 percent_left_b2 > .9 |
                                 percent_left_b3 < .1 |
                                 percent_left_b3 > .9 |
                                 answers_incorrect > 2)

#count the number of soft QC cutoffs each subject meets
subs$softs <- 0
for(i in 1:nrow(subs)){
  subs$softs[i] <- length(which(c(subs$att_checks_passed[i] == 5,subs$valrat_skipped_percent[i] > .05, subs$late_percent[i] > .15,
                                  subs$sd_valrat[i] < .1, subs$percent_left[i] > .75, subs$percent_left[i] < .25,
                                  subs$percent_left_b1[i] > .85, subs$percent_left_b1[i] < .15, subs$percent_left_b2[i] > .85, 
                                  subs$percent_left_b2[i] < .15,subs$percent_left_b3[i] > .85, subs$percent_left_b3[i] < .15,subs$answers_incorrect[i] > 1)))
}

sub_soft_fail <- filter(subs,softs >= 2) #identify those who meet more than 2 soft cutoffs

subs_to_exclude <- unique(c(sub_hard_fail$id,sub_soft_fail$id)) #get subjects who failed either set of criteria

#clean data
trials <- trials %>% filter(!(id %in% subs_to_exclude)) %>% filter(choice != "late") 
subs <- subs %>% filter(!(id %in% subs_to_exclude))

length(subs_to_exclude)/(nrow(subs)+length(subs_to_exclude)) #get percent excluded
```

Data transformations
```{r}
trials <- add_sub_indices(trials) #add subject indices to the df. These will match the indices used in Stan.
trials <- add_probe_number(trials,newcol="rat_number",val_col="valrat_z") #add rating number

#add a column with completed trial numbers - the trial indices if you ignore late trials. These will match the "t" trial numbers used in the Stan models
trials <- do.call(rbind,by(trials,trials$sub_index,add_trials_nl))
trials$overall_trial_nl <- 1:nrow(trials) #get the overall trial number ignoring late trials and collapsing across subjects

#Create indices from 1:n_f for each fractal image. To do this, first create a mini-df with one column having all the fA_img values and the other two
#columns having indices for fA and fB. This assumes that every fA_img is paired with a unique fB_img.
f_index_df <- data.frame(fA_img = unique(trials$fA_img),fA_ix = 1:length(unique(trials$fA_img)),fB_ix = (1:length(unique(trials$fA_img))+length(unique(trials$fA_img))))
trials <- left_join(trials,f_index_df,by="fA_img")

#get the chosen fractal index
trials <- trials %>% mutate(chosen_frac = ifelse(choice == "fA",fA_ix,fB_ix))
trials <- trials %>% mutate(unchosen_frac = ifelse(choice == "fA",fB_ix,fA_ix))
```

# Data review

```{r}
dr_vars <- c("valreg_rsq","bv_b","fres_b","fres_bv_ratio")
plot_sub_level_vars(subs,dr_vars,path_to_project_directory,type="dr") #create and save plot grids
```

```{r}
subs$age <- as.numeric(subs$age)
age_no_skips <- filter(subs,age < 900)
plot_hist(age_no_skips,"age") 
```

```{r}
sum(subs$gender=="Male")
```

```{r}
sum(subs$gender=="Female")
```

```{r}
sum(subs$gender=="Non-binary")
```

```{r}
sub_age <- subs %>% filter(age < 80)
mean(sub_age$age)
sd(sub_age$age)
```

```{r}
trials$pair_pres_num <- rep(c(1:48),323*3)
percentage_plots(trials,"stay")
```

# Preregistered analyses

Fit first couple of models
```{r}
one_q <- fit_stan_model(stan_file=paste0(stan_model_dir,"one_q.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   n_t = 144)
```

Fit no-choice-autocorrelation version of one_q
```{r}
one_q_nocac <- fit_stan_model(stan_file=paste0(stan_model_dir,"one_q_nocac.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   n_t = 144)
```

Check diagnostics
```{r}
one_q$diagnostics
one_q_nocac$diagnostics
```


```{r}
one_q <- read_fsml("one_q",model_out_dir = model_out_dir)
fsml_compare(one_q,one_q_nocac)
```
Autocorrelation clearly helps

Predict choice with Q, A, S, B, and V.
```{r}
two_q <- fit_stan_model(stan_file=paste0(stan_model_dir,"two_q.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "s3",
                                   n_t = 144)
```

```{r}
two_q$diagnostics
```
Ok

Compare
```{r}
fsml_compare(one_q,two_q)
```
Looks like two_q fits better

Does this show up in the learning and forgetting rates?
```{r}
twoq_lrn_dc_draws <- get_draws("two_q",model_out_dir=model_out_dir,vars=c("lrn_fr_mu","lrn_nf_mu","dcy_fr_mu","dcy_nf_mu"))
mcmc_areas(
  lfsm_draws,
  area_method = "scaled height",
  prob = 0.5,
  prob_outer = .95, 
  point_est = "median"
)
```

```{r}
sigmoid(filt_sum(two_q$sum,"lrn_fr_mu")$median)
sigmoid(filt_sum(two_q$sum,"lrn_nf_mu")$median)
(sigmoid(twoq_lrn_dc_draws[,,"lrn_fr_mu"]) - sigmoid(twoq_lrn_dc_draws[,,"lrn_nf_mu"])) > 0
```
Indeed, the learning rate is higher for fres than no-fres trials, as predicted.

Fit winner with side bias
```{r}
two_q_sidebias <- fit_stan_model(stan_file=paste0(stan_model_dir,"two_q_sidebias.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   chains = 4,
                                   n_t = 144)
```

Compare
```{r}
fsml_compare(two_q,two_q_sidebias)
```

The model with side bias fits better. HOWEVER, you initially thought that the model without side bias fit
better, and you proceeded on that assumption. Below are analyses based on that faulty assumption. Under "Side
Bias reanalysis", you rerun analyses to reflect the fact that the model should include side bias, after all.

Testing effects of reward and affect associations on choice in two_q model
```{r}
twoq_aff <- get_draws("two_q",vars=c("scd_aff_fr_sens_mu"))
quantile(twoq_aff,c(.025,.5,.975))
mean(twoq_aff > 0)

twoq_rew <- get_draws("two_q",vars=c("scd_rew_fr_sens_mu"))
quantile(twoq_rew,c(.025,.5,.975))
mean(twoq_rew > 0)
```


# Exploratory analyses

## Momentum model
Momentum model
```{r}
mom_rat <- fit_stan_model(stan_file=paste0(stan_model_dir,"mom_rat.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   chains = 3,
                                   n_t = 144)
```

```{r}
mom_terms <- get_draws("mom_rat",model_out_dir=model_out_dir,vars=c("x_sens_mu","aff_fr_sens_mu","B_auto_mu"))
mcmc_areas(
  mom_terms,
  pars = "x_sens_mu",
  area_method = "scaled height",
  prob = 0.9,
  prob_outer = .99, 
  point_est = "median"
)
total_mom <- mom_terms[,,"x_sens_mu"] + mom_terms[,,"aff_fr_sens_mu"]*mom_terms[,,"B_auto_mu"]
mcmc_areas(
  total_mom,
  area_method = "scaled height",
  prob = 0.9,
  prob_outer = .99, 
  point_est = "median"
)
```

## Separating modeled and residual affect

Predict RL using model-predicted affect, and residual affect, with a fuller affect model
```{r}
mod_aff_resid <- fit_stan_model(stan_file=paste0(stan_model_dir,"mod_aff_resid.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   chains = 3,
                                   n_t = 144)
```

```{r}
mom_sens_draws <- get_draws("mod_aff_resid",model_out_dir=model_out_dir,vars=c("aff_fr_sens_mu","rew_fr_sens_mu","resid_fr_sens_mu"))
mcmc_areas(
  mom_sens_draws,
  pars = "aff_fr_sens_mu",
  area_method = "scaled height",
  prob = 0.9,
  prob_outer = .99, 
  point_est = "median"
)
```

Is this a stronger effect than what we had before?
```{r}
twoq_int_draws <- get_draws("two_q",model_out_dir=model_out_dir,vars=c("aff_fr_sens_mu"))

m_vs_rat <- mom_sens_draws[,,"aff_fr_sens_mu"] - twoq_int_draws[,,"aff_fr_sens_mu"]
quantile(m_vs_rat,probs=c(.01,.025,.05,.5,.95,.975,.99))

m_vs_resid <- mom_sens_draws[,,"aff_fr_sens_mu"] - mom_sens_draws[,,"resid_fr_sens_mu"]
quantile(m_vs_resid,probs=c(.01,.025,.05,.5,.95,.975,.99))
```


```{r}
mcmc_areas(
  mom_sens_draws,
  pars = "rew_fr_sens_mu",
  area_method = "scaled height",
  prob = 0.9,
  prob_outer = .99, 
  point_est = "median"
)
```

```{r}
mcmc_areas(
  mom_sens_draws,
  pars = "resid_fr_sens_mu",
  area_method = "scaled height",
  prob = 0.9,
  prob_outer = .99, 
  point_est = "median"
)
```

```{r}
filt_sum(mod_aff_resid$sum,"mu")
```

Now, breaking things down further: separately estimating effects of modeled affect, residual affect, and nuisance variation.
```{r}
breakdown <- fit_stan_model(stan_file=paste0(stan_model_dir,"breakdown.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   n_t = 144,
                                   iter_sampling = 6000)
```

```{r}
filt_sum(breakdown$sum,"mu")
filt_sum(mod_aff_resid$sum,"mu")
```
Looks like it was worthwhile to break the result down like this - it resulted in much stronger estimates for aff_fres and allowed the effect of nuisance affect to be what it is.

```{r}
fsml_compare(breakdown,mod_aff_resid)
```

```{r}
breakdown_ma_sens <- get_draws("breakdown",vars=c("scd_ma_fr_sens_mu"))
quantile(breakdown_ma_sens,probs=c(.025,.5,.975))
breakdown_rew_sens <- get_draws("breakdown",vars=c("scd_rew_fr_sens_mu"))
quantile(breakdown_rew_sens,probs=c(.025,.5,.975))
quantile(breakdown_ma_sens - breakdown_rew_sens,probs=c(.025,.5,.975))
mean(breakdown_ma_sens > breakdown_rew_sens)
breakdown_resid_sens <- get_draws("breakdown",vars=c("scd_resid_fr_sens_mu"))
quantile(breakdown_resid_sens,probs=c(.025,.5,.975))
```


Next, just running a model with separate effects of model-predicted and residual valence on choice, not including
the orthogonal nuisance affect, for simplicity.
```{r}
mod_resid_sep <- fit_stan_model(stan_file=paste0(stan_model_dir,"mod_resid_sep.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   n_t = 144)
```

Rerunning this model with more iterations, and renaming it "final"
```{r}
final <- fit_stan_model(stan_file=paste0(stan_model_dir,"final.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   n_t = 144,
                                   skip=c("check_csvs","loo"),
                                   iter_sampling = 6000)
```

Getting effect estimates from the "final" model
```{r}
final_Bbv <- get_draws("final",vars=c("B_bv_fr_mu"))
final_Brew <- get_draws("final",vars=c("B_rew_fr_mu"))
final_rew <- get_draws("final",vars=c("scd_rew_fr_sens_mu"))
final_aff <- get_draws("final",vars=c("scd_aff_fr_sens_mu"))
final_resid <- get_draws("final",vars=c("scd_resid_fr_sens_mu"))
val_mod_rsq <- get_draws("final",vars=c("val_mod_rsq"))
```

```{r}
trials_fres <- filter(trials,show_fres==1)
final_Bbv_scd <- sd(trials_fres$box_val)*final_Bbv
quantile(final_Bbv_scd,c(.025,.5,.975))
mean(final_Bbv_scd < 1)
```

```{r}
final_Brew_scd <- sd(trials_fres$out)*final_Brew
quantile(final_Brew_scd,c(.025,.5,.975))
mean(final_Brew_scd > 1)
```


```{r}
quantile(final_aff-final_rew,c(.025,.5,.975))
mean(final_aff > final_rew)
quantile(final_aff,c(.025,.5,.975))
mean(final_aff > 0)
quantile(final_rew,c(.025,.5,.975))
mean(final_rew > 0)
```

```{r}
quantile(final_resid,c(.025,.5,.975))
mean(final_resid > 0)

quantile(final_aff-final_resid,c(.025,.5,.975))
mean(final_aff > final_resid)
```

getting r-squared value
```{r}
median(val_mod_rsq)
```

# Side bias reanalysis

After re-doing the model comparison between the one_q, two_q, and two_q_sidebias models, I realized that
two_q_sidebias actually fit better. So below you rerun analyses accordingly.

## New model
```{r}
final_ls <- fit_stan_model(stan_file=paste0(stan_model_dir,"final_ls.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   n_t = 144,
                                   skip=c("check_csvs","loo"),
                                   iter_sampling = 6000)
```

```{r}
scd_aff_fr_sens_mu <- get_draws("final_ls",vars=c("scd_aff_fr_sens_mu"),model_out_dir=model_out_dir)
scd_rew_fr_sens_mu <- get_draws("final_ls",vars=c("scd_rew_fr_sens_mu"),model_out_dir=model_out_dir)
quantile(scd_aff_fr_sens_mu-scd_rew_fr_sens_mu,c(.025,.5,.975))
mean(scd_aff_fr_sens_mu > scd_rew_fr_sens_mu)
```


Creating interval plot
```{r}
bq_ba_array <- abind(scd_rew_fr_sens_mu,scd_aff_fr_sens_mu,along=3)
bq_bq_intervals <- create_interval_plot(arr = bq_ba_array,names = c("scd_rew_fr_sens_mu","scd_aff_fr_sens_mu"),
                                          xmin = -.012,xmax = .65, percentiles = c(.05,.25,.50,.75,.95)) +
                        theme(panel.grid.major.x = element_line(color = "#DCDCDC", size = .47),
                              panel.background = element_rect(fill = "white", color = NA),
                              axis.text.x = element_blank(),
                              axis.text.y=element_blank()) 
                        
bq_bq_intervals
ggsave("/Users/dp/Documents/conferences/SASolina_2025/figures/bq_bq_intervals_s3.pdf",bq_bq_intervals,width=2,height=1)
```

Compare the population-mean effects of chosen reward associations and box amounts on affective responses
when cue outcomes were received
```{r}
# Read the saved final_ls summary so the comparison uses the fitted population-level parameters.
s3_aff_resp_sum <- read_fsml("final_ls", model_out_dir = model_out_dir)$sum

# Pull one parameter row from the summary table, failing loudly if the requested name is absent.
s3_aff_resp_param <- function(param_name) {
  param_row <- s3_aff_resp_sum %>% filter(variable == param_name)
  if (nrow(param_row) != 1) {
    stop(paste0("Could not find exactly one final_ls summary row for ", param_name, "."))
  }
  param_row
}

# Use the population means for the reward-association update rule. These are on the logit scale in Stan.
s3_aff_resp_lrn_fr <- sigmoid(s3_aff_resp_param("lrn_fr_mu")$mean)
s3_aff_resp_dcy_fr <- sigmoid(s3_aff_resp_param("dcy_fr_mu")$mean)

# Recreate the chosen reward association that enters the final_ls affective-response model.
# This isolates the B_q_fr_mu * Q_fr_ch term, separate from the probability-weighted Q term.
s3_aff_resp_n_f <- length(unique(c(trials$fA_ix, trials$fB_ix)))
s3_aff_resp_assoc <- trials %>%
  arrange(sub_index, overall_trial_nl) %>%
  select(sub_index, overall_trial_nl, chosen_frac, show_fres, out, box_val, rat_number, valrat_z) %>%
  mutate(
    lrn_fr = s3_aff_resp_lrn_fr,
    dcy_fr = s3_aff_resp_dcy_fr
  ) %>%
  split(.$sub_index) %>%
  lapply(
    add_assoc,
    cue_cols = "chosen_frac",
    out_cols = "out",
    update_col = "show_fres",
    num_assoc = s3_aff_resp_n_f,
    assoc_name = "rew_fr",
    lrn_rate = "lrn_fr",
    for_rate = "dcy_fr"
  ) %>%
  bind_rows() %>%
  arrange(sub_index, overall_trial_nl)

# Pull the current-trial value of the chosen cue's reward association.
s3_aff_resp_assoc_mat <- as.matrix(s3_aff_resp_assoc[paste0("rew_fr_", 1:s3_aff_resp_n_f)])
s3_aff_resp_assoc$r_ch <- s3_aff_resp_assoc_mat[
  cbind(seq_len(nrow(s3_aff_resp_assoc)), s3_aff_resp_assoc$chosen_frac)
]

# Limit the empirical predictor scales to trials that actually contribute affective responses to cue outcomes.
s3_aff_resp_fres <- s3_aff_resp_assoc %>%
  filter(show_fres == 1, rat_number != 0, !is.na(valrat_z))

# Gather the fitted population effects for the two focal predictors in the outcome-present rating equation.
s3_aff_resp_effects <- bind_rows(
  s3_aff_resp_param("B_q_fr_mu") %>%
    mutate(predictor = "r_ch", predictor_label = "Chosen reward association"),
  s3_aff_resp_param("B_bv_fr_mu") %>%
    mutate(predictor = "box_val", predictor_label = "Box amount")
) %>%
  select(predictor, predictor_label, parameter = variable, effect_mean = mean, effect_q5 = q5, effect_q95 = q95)

# Put the raw population effects onto the empirical predictor scales seen on outcome-present rating trials.
s3_aff_resp_scales <- s3_aff_resp_fres %>%
  summarize(
    r_ch_sd = sd(r_ch),
    r_ch_range = max(r_ch) - min(r_ch),
    box_val_sd = sd(box_val),
    box_val_range = max(box_val) - min(box_val)
  ) %>%
  pivot_longer(
    everything(),
    names_to = c("predictor", ".value"),
    names_pattern = "(r_ch|box_val)_(sd|range)"
  )

s3_aff_resp_comparison <- s3_aff_resp_effects %>%
  left_join(s3_aff_resp_scales, by = "predictor") %>%
  mutate(
    mean_effect_1sd = effect_mean * sd,
    q5_effect_1sd = effect_q5 * sd,
    q95_effect_1sd = effect_q95 * sd,
    mean_effect_range = effect_mean * range,
    q5_effect_range = effect_q5 * range,
    q95_effect_range = effect_q95 * range
  )

# Express the comparison as absolute r_ch-to-box ratios, since the two raw predictors have different units.
s3_aff_resp_ratio <- s3_aff_resp_comparison %>%
  summarize(
    abs_rch_to_box_1sd = abs(mean_effect_1sd[predictor == "r_ch"]) /
      abs(mean_effect_1sd[predictor == "box_val"]),
    abs_rch_to_box_range = abs(mean_effect_range[predictor == "r_ch"]) /
      abs(mean_effect_range[predictor == "box_val"])
  )

s3_aff_resp_comparison
s3_aff_resp_ratio
```


I think you redid some of the stats but didn't put them in the markdown. Oh well. These analyses are in the
manuscript repo, at least.

Fitting at 1000 iterations so it can be compared to two_q_sidebias, and so it finishes running quicker
```{r}
final_ls_test <- fit_stan_model(stan_file=paste0(stan_model_dir,"final_ls_test.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   n_t = 144)
```

```{r}
fsml_compare(final_ls_test,two_q_sidebias)
```

## Getting results from two_q_sidebias

```{r}
aff_twoq_side <- get_draws("two_q_sidebias",vars=c("scd_aff_fr_sens_mu"),model_out_dir=model_out_dir)
rew_twoq_side <- get_draws("two_q_sidebias",vars=c("scd_rew_fr_sens_mu"),model_out_dir=model_out_dir)

cat("Effect of reward associations on choice\n")
quantile(rew_twoq_side,c(.50,.025,.975))
round(mean(rew_twoq_side > 0) * 100,1)

cat("Effect of affect associations on choice\n")
quantile(aff_twoq_side,c(.50,.025,.975))
round(mean(aff_twoq_side > 0) * 100,1)
```

# Regressing valence and reward onto choice

Do a model-free test of whether valence and reward both predict choice
```{r}
trials_fres <- filter(trials,show_fres == 1)
trials_fres_scale <- trials_fres %>% mutate(valrat_z=scale(valrat_z),out=scale(out))
stay_fit <- lmer(stay ~ valrat_z + out + (valrat_z + out | sub_index),trials_fres_scale)
summary(stay_fit)
confint(stay_fit, parm = c("valrat_z","out"))
```

Do a quick model-free test of whether participants are more likely to choose the left-side cue when its most
recent cue outcome, or the box amount present when that cue was most recently chosen, was better than the
right-side cue's.
```{r}
# Add raw, last-choice predictors for the two cues shown on each trial.
#
# The function walks through one subject's trials in order. Before each choice, it stores the cue
# outcome from the last time the left and right cues were chosen, plus the box amount that was
# present on those same prior choices. The histories are pre-choice predictors: the current trial
# updates the stored values only after its predictors have been recorded.
add_last_chosen_cue_experience <- function(sub_trials) {
  sub_trials <- sub_trials %>% arrange(block, trial_nl)
  
  # Initialize cue-specific histories. Each block uses a new cue pair, so histories reset at block starts.
  n_frac <- max(c(sub_trials$fA_ix, sub_trials$fB_ix), na.rm = TRUE)
  last_out <- rep(NA_real_, n_frac)
  last_box <- rep(NA_real_, n_frac)
  current_block <- NA_real_
  
  # Allocate trial-level columns that will be used in the choice regression.
  sub_trials$last_out_fA <- NA_real_
  sub_trials$last_out_fB <- NA_real_
  sub_trials$last_box_fA <- NA_real_
  sub_trials$last_box_fB <- NA_real_
  
  for(row in seq_len(nrow(sub_trials))) {
    # Reset histories when a new block begins, because cue identities do not carry across blocks.
    if(is.na(current_block) || sub_trials$block[row] != current_block) {
      last_out <- rep(NA_real_, n_frac)
      last_box <- rep(NA_real_, n_frac)
      current_block <- sub_trials$block[row]
    }
    
    # Store the left and right cues' histories before observing the current trial's outcome.
    fA <- sub_trials$fA_ix[row]
    fB <- sub_trials$fB_ix[row]
    sub_trials$last_out_fA[row] <- last_out[fA]
    sub_trials$last_out_fB[row] <- last_out[fB]
    sub_trials$last_box_fA[row] <- last_box[fA]
    sub_trials$last_box_fB[row] <- last_box[fB]
    
    # Update the chosen cue's history from this choice, regardless of whether this trial is later
    # used in the regression. The outcome and box amount come from the same most-recent choice.
    chosen_frac <- sub_trials$chosen_frac[row]
    if(!is.na(chosen_frac)) {
      last_out[chosen_frac] <- sub_trials$out[row]
      last_box[chosen_frac] <- sub_trials$box_val[row]
    }
  }
  
  sub_trials
}

# Build the regression dataset from pre-choice history differences.
choice_last_experience <- trials %>%
  split(.$sub_index) %>%
  lapply(add_last_chosen_cue_experience) %>%
  bind_rows() %>%
  mutate(choice_fA = ifelse(choice == "fA", 1, 0),
         last_out_diff = last_out_fA - last_out_fB,
         last_box_diff = last_box_fA - last_box_fB) %>%
  filter(!is.na(last_out_diff), !is.na(last_box_diff))

# Summarize the available trials before fitting, since early trials lack history for one or both cues.
choice_last_experience %>%
  summarize(n = n(),
            prop_choose_fA = mean(choice_fA),
            mean_last_out_diff = mean(last_out_diff),
            mean_last_box_diff = mean(last_box_diff))

# Test whether raw cue-outcome and box-amount histories predict left-side cue choices.
last_experience_choice_fit <- glmer(
  choice_fA ~ last_out_diff + last_box_diff + (last_out_diff + last_box_diff | sub_index),
  data = choice_last_experience,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa")
)
summary(last_experience_choice_fit)
confint(last_experience_choice_fit, parm = c("last_out_diff","last_box_diff"), method = "Wald")
```

Model amputation check: simulate choices from the `final_ls` posterior with and without the `A_fr` effect on
choice, then compare the posterior predictive choice summaries to the observed choice summaries.
```{r, eval=FALSE}
# Set a small value for quick debugging; use ~500 for the manuscript version.
s3_amp_n_draws <- 100
s3_amp_seed <- 19

# Create a timestamped output directory so reruns do not overwrite prior simulations.
s3_amp_dir <- paste0(path_to_project_directory, "output/amputation/")
if (!dir.exists(s3_amp_dir)) {
  dir.create(s3_amp_dir, recursive = TRUE)
}
s3_amp_timestamp <- format(Sys.time(), "%Y%m%d_%H%M%S")

# Build the fixed trial scaffold used to replay observed choices, outcomes, and ratings.
s3_amp_template <- s3_prepare_amputation_template(trials)
s3_amp_sub_ids <- sort(unique(s3_amp_template$sub_index))

# Read the needed final_ls posterior draws once; this is the slow disk I/O step.
s3_amp_fit_draws <- s3_read_amputation_draws(
  model = "final_ls",
  model_out_dir = model_out_dir
)

# Reconstruct subject-level parameters from the already-read posterior draws.
s3_amp_params <- s3_sample_amputation_subject_params(
  fit_draws = s3_amp_fit_draws,
  sub_ids = s3_amp_sub_ids,
  n_draws = s3_amp_n_draws,
  seed = s3_amp_seed
)

# Replay observed histories and save compact summaries under full and A_fr-amputated policies.
s3_amp_summary_set <- s3_run_replay_amputation_summary_set(
  trial_template = s3_amp_template,
  subject_params = s3_amp_params
)

# Summarize observed and posterior-predictive realized stay probabilities.
s3_amp_observed_summary <- s3_observed_stay_summary(s3_amp_template)
s3_amp_sim_draw_summary <- s3_amp_summary_set$sim_draw_summary
s3_amp_sim_summary <- s3_simulated_interval_summary(s3_amp_sim_draw_summary)
s3_amp_p_values <- s3_observed_stay_p_values(s3_amp_template)
s3_amp_plot_summary <- bind_rows(s3_amp_observed_summary, s3_amp_sim_summary)

# Summarize the policy-implied probability of staying, which avoids simulated-choice noise.
s3_amp_pred_draw_summary <- s3_amp_summary_set$pred_draw_summary
s3_amp_pred_summary <- s3_simulated_interval_summary(s3_amp_pred_draw_summary)
s3_amp_pred_plot_summary <- bind_rows(s3_amp_observed_summary, s3_amp_pred_summary)

# Summarize overall stay calibration before interpreting condition-specific patterns.
s3_amp_observed_overall <- s3_observed_overall_stay_summary(s3_amp_template)
s3_amp_overall_draw_summary <- s3_amp_summary_set$overall_draw_summary
s3_amp_overall_summary <- s3_overall_interval_summary(s3_amp_overall_draw_summary)
s3_amp_overall_calibration <- bind_rows(s3_amp_observed_overall, s3_amp_overall_summary)
s3_amp_overall_calibration

# Save compact outputs; the full trial-level simulation is intentionally not saved by default.
s3_amp_prefix <- paste0(s3_amp_dir, "s3_af_amputation_", s3_amp_n_draws, "draws_", s3_amp_timestamp)
write.csv(s3_amp_observed_summary, paste0(s3_amp_prefix, "_observed_summary.csv"), row.names = FALSE)
write.csv(s3_amp_sim_draw_summary, paste0(s3_amp_prefix, "_sim_draw_summary.csv"), row.names = FALSE)
write.csv(s3_amp_sim_summary, paste0(s3_amp_prefix, "_sim_interval_summary.csv"), row.names = FALSE)
write.csv(s3_amp_pred_draw_summary, paste0(s3_amp_prefix, "_pred_draw_summary.csv"), row.names = FALSE)
write.csv(s3_amp_pred_summary, paste0(s3_amp_prefix, "_pred_interval_summary.csv"), row.names = FALSE)
write.csv(s3_amp_overall_calibration, paste0(s3_amp_prefix, "_overall_calibration.csv"), row.names = FALSE)
write.csv(s3_amp_p_values, paste0(s3_amp_prefix, "_observed_p_values.csv"), row.names = FALSE)
saveRDS(
  list(
    n_draws = s3_amp_n_draws,
    seed = s3_amp_seed,
    observed_summary = s3_amp_observed_summary,
    sim_draw_summary = s3_amp_sim_draw_summary,
    sim_summary = s3_amp_sim_summary,
    pred_draw_summary = s3_amp_pred_draw_summary,
    pred_summary = s3_amp_pred_summary,
    overall_calibration = s3_amp_overall_calibration,
    observed_p_values = s3_amp_p_values
  ),
  paste0(s3_amp_prefix, "_summary_objects.rds")
)

# Plot realized simulated stay rates with a zoomed y-axis.
s3_amp_plot <- plot_s3_amputation_stay(
  summary_df = s3_amp_plot_summary,
  p_values = s3_amp_p_values
)
s3_amp_plot
ggsave(paste0(s3_amp_prefix, "_stay_probability_plot.pdf"), s3_amp_plot, width = 6.2, height = 3.3)

# Plot policy-implied p(stay); note the truncated y-axis in the manuscript caption.
s3_amp_pred_plot <- plot_s3_amputation_stay(
  summary_df = s3_amp_pred_plot_summary,
  p_values = s3_amp_p_values
)
s3_amp_pred_plot
ggsave(paste0(s3_amp_prefix, "_predicted_stay_probability_plot.pdf"), s3_amp_pred_plot, width = 6.2, height = 3.3)
```

Posterior-mean subject-level parameter version of the same policy-implied stay-probability check. This skips
binary choice simulation and summarizes only model-implied `p(stay)`.
```{r, eval=FALSE}
# Recreate shared setup objects if this chunk is run without first running the replay chunk.
if (!exists("s3_amp_dir")) {
  s3_amp_dir <- paste0(path_to_project_directory, "output/amputation/")
}
if (!dir.exists(s3_amp_dir)) {
  dir.create(s3_amp_dir, recursive = TRUE)
}
if (!exists("s3_amp_timestamp")) {
  s3_amp_timestamp <- format(Sys.time(), "%Y%m%d_%H%M%S")
}
if (!exists("s3_amp_template")) {
  s3_amp_template <- s3_prepare_amputation_template(trials)
}
if (!exists("s3_amp_sub_ids")) {
  s3_amp_sub_ids <- sort(unique(s3_amp_template$sub_index))
}
if (!exists("s3_amp_observed_summary")) {
  s3_amp_observed_summary <- s3_observed_stay_summary(s3_amp_template)
}
if (!exists("s3_amp_observed_overall")) {
  s3_amp_observed_overall <- s3_observed_overall_stay_summary(s3_amp_template)
}
if (!exists("s3_amp_observed_last_experience_choice")) {
  s3_amp_observed_last_experience_choice <- s3_observed_last_experience_choice_summary(s3_amp_template)
}
if (!exists("s3_amp_p_values")) {
  s3_amp_p_values <- s3_observed_stay_p_values(s3_amp_template)
}

# Reconstruct subject-level mean parameters from the saved final_ls summary table.
final_ls_sum <- read_fsml("final_ls", model_out_dir = model_out_dir)$sum
s3_amp_mean_params <- s3_summary_mean_subject_params(
  sum_df = final_ls_sum,
  sub_ids = s3_amp_sub_ids
)

# Evaluate full and A_fr-amputated policies along observed histories.
s3_amp_mean_policy_set <- s3_run_replay_policy_amputation_summary_set(
  trial_template = s3_amp_template,
  subject_params = s3_amp_mean_params
)

# Summarize and save the probability-scale output.
s3_amp_mean_pred_draw_summary <- s3_amp_mean_policy_set$pred_draw_summary
s3_amp_mean_pred_summary <- s3_simulated_interval_summary(s3_amp_mean_pred_draw_summary)
s3_amp_mean_pred_plot_summary <- bind_rows(s3_amp_observed_summary, s3_amp_mean_pred_summary)

s3_amp_mean_overall_summary <- s3_overall_interval_summary(s3_amp_mean_policy_set$overall_draw_summary)
s3_amp_mean_overall_calibration <- bind_rows(s3_amp_observed_overall, s3_amp_mean_overall_summary)
s3_amp_mean_overall_calibration

s3_amp_mean_prefix <- paste0(s3_amp_dir, "s3_af_amputation_posterior_mean_policy_", s3_amp_timestamp)
write.csv(s3_amp_mean_pred_draw_summary, paste0(s3_amp_mean_prefix, "_pred_draw_summary.csv"), row.names = FALSE)
write.csv(s3_amp_mean_pred_summary, paste0(s3_amp_mean_prefix, "_pred_interval_summary.csv"), row.names = FALSE)
write.csv(s3_amp_mean_overall_calibration, paste0(s3_amp_mean_prefix, "_overall_calibration.csv"), row.names = FALSE)
saveRDS(
  list(
    pred_draw_summary = s3_amp_mean_pred_draw_summary,
    pred_summary = s3_amp_mean_pred_summary,
    overall_calibration = s3_amp_mean_overall_calibration
  ),
  paste0(s3_amp_mean_prefix, "_summary_objects.rds")
)

# Plot posterior-mean policy-implied p(stay); no binary simulated choices are used.
s3_amp_mean_pred_plot <- plot_s3_amputation_stay(
  summary_df = s3_amp_mean_pred_plot_summary,
  p_values = s3_amp_p_values
)
s3_amp_mean_pred_plot
ggsave(paste0(s3_amp_mean_prefix, "_predicted_stay_probability_plot.pdf"), s3_amp_mean_pred_plot, width = 6.2, height = 3.3)
```

Closed-loop version of the same amputation check. Here, simulated choices feed back into future reward,
affect, residual, and choice-autocorrelation histories.
```{r, eval=FALSE}
# Recreate shared setup objects if this chunk is run without first running the replay chunk.
if (!exists("s3_amp_dir")) {
  s3_amp_dir <- paste0(path_to_project_directory, "output/amputation/")
}
if (!dir.exists(s3_amp_dir)) {
  dir.create(s3_amp_dir, recursive = TRUE)
}
if (!exists("s3_amp_timestamp")) {
  s3_amp_timestamp <- format(Sys.time(), "%Y%m%d_%H%M%S")
}
if (!exists("s3_amp_template")) {
  s3_amp_template <- s3_prepare_amputation_template(trials)
}
if (!exists("s3_amp_sub_ids")) {
  s3_amp_sub_ids <- sort(unique(s3_amp_template$sub_index))
}
if (!exists("s3_amp_observed_summary")) {
  s3_amp_observed_summary <- s3_observed_stay_summary(s3_amp_template)
}
if (!exists("s3_amp_observed_overall")) {
  s3_amp_observed_overall <- s3_observed_overall_stay_summary(s3_amp_template)
}
if (!exists("s3_amp_observed_last_experience_choice")) {
  s3_amp_observed_last_experience_choice <- s3_observed_last_experience_choice_summary(s3_amp_template)
}
if (!exists("s3_amp_p_values")) {
  s3_amp_p_values <- s3_observed_stay_p_values(s3_amp_template)
}

# Reuse s3_amp_fit_draws/s3_amp_params from the replay chunk when available.
if (!exists("s3_amp_fit_draws")) {
  s3_amp_fit_draws <- s3_read_amputation_draws(
    model = "final_ls",
    model_out_dir = model_out_dir
  )
}
if (!exists("s3_amp_params")) {
  s3_amp_params <- s3_sample_amputation_subject_params(
    fit_draws = s3_amp_fit_draws,
    sub_ids = s3_amp_sub_ids,
    n_draws = s3_amp_n_draws,
    seed = s3_amp_seed
  )
}

# Build posterior-median Q and M differences from the final_ls_m_val posterior.
#
# These helpers reconstruct the observed-history Q and M recursions from the posterior draws
# of the FR learning and decay parameters. The resulting x-axis is fixed across the observed,
# full closed-loop, and A_fr-amputated lines, so differences among lines reflect choice behavior
# rather than different x-axis histories.
s3_flatten_posterior_draws <- function(draws_obj) {
  # Accept either the usual iterations x chains x variables array or an already-flattened matrix.
  if (length(dim(draws_obj)) == 3) {
    flat_draws <- matrix(
      draws_obj,
      nrow = dim(draws_obj)[1] * dim(draws_obj)[2],
      ncol = dim(draws_obj)[3]
    )
    colnames(flat_draws) <- dimnames(draws_obj)[[3]]
  } else {
    flat_draws <- as.matrix(draws_obj)
  }
  
  flat_draws
}

# Return the column name used by CmdStan for one element of a subject-level vector.
# Most project CSVs use dot notation (e.g., lrn_fr_z.1), but the bracket fallback
# makes the helper a bit more tolerant of alternate draw formats.
s3_stan_vector_col <- function(draw_names, base_name, index) {
  candidates <- c(
    paste0(base_name, ".", index),
    paste0(base_name, "[", index, "]")
  )
  matched <- candidates[candidates %in% draw_names]
  if (length(matched) == 0) {
    stop(paste0("Could not find ", base_name, " for subject index ", index, " in final_ls_m_val draws."))
  }
  
  matched[1]
}

# Compute Q and M left-minus-right differences for one subject under one posterior draw.
# This mirrors the final_ls_m_val recurrence: values are read before the current choice,
# unchosen cues decay toward 0, and the chosen cue is updated on feedback trials.
s3_subject_qm_diff_for_draw <- function(sub_design, lrn_fr, dcy_fr, n_f) {
  sub_design <- sub_design %>% arrange(overall_trial_nl)
  q_fr <- rep(0, n_f)
  m_fr <- rep(0, n_f)
  q_diff <- rep(NA_real_, nrow(sub_design))
  m_diff <- rep(NA_real_, nrow(sub_design))
  
  for (trial_ix in seq_len(nrow(sub_design))) {
    # Store pre-choice Q and M differences for the two currently presented cues.
    cue_a <- sub_design$fA_ix[trial_ix]
    cue_b <- sub_design$fB_ix[trial_ix]
    q_diff[trial_ix] <- q_fr[cue_a] - q_fr[cue_b]
    m_diff[trial_ix] <- m_fr[cue_a] - m_fr[cue_b]
    
    # Prepare next-trial values: all cues decay, then the chosen feedback cue updates.
    q_next <- (1 - dcy_fr) * q_fr
    m_next <- (1 - dcy_fr) * m_fr
    if (!is.na(sub_design$show_fres[trial_ix]) && sub_design$show_fres[trial_ix] == 1) {
      chosen_frac <- sub_design$chosen_frac[trial_ix]
      q_next[chosen_frac] <- q_fr[chosen_frac] + lrn_fr * (sub_design$out[trial_ix] - q_fr[chosen_frac])
      m_next[chosen_frac] <- m_fr[chosen_frac] + lrn_fr * (sub_design$box_val[trial_ix] - m_fr[chosen_frac])
    }
    
    q_fr <- q_next
    m_fr <- m_next
  }
  
  list(q_diff = q_diff, m_diff = m_diff)
}

# Reconstruct posterior-median trialwise Q and M differences from final_ls_m_val draws.
# To keep memory bounded, the function computes medians subject-by-subject instead of
# storing all posterior draws for all trials at once.
s3_build_mval_qm_predictors <- function(trial_template, mval_learning_draws, n_draws = NULL, seed = NULL) {
  draw_mat <- s3_flatten_posterior_draws(mval_learning_draws)
  sub_ids <- sort(unique(trial_template$sub_index))
  n_f <- max(c(trial_template$fA_ix, trial_template$fB_ix), na.rm = TRUE)
  
  # Optionally use a reproducible subset for quick checks; NULL uses every available draw.
  if (!is.null(n_draws) && n_draws < nrow(draw_mat)) {
    if (!is.null(seed)) {
      set.seed(seed)
    }
    draw_mat <- draw_mat[sample(seq_len(nrow(draw_mat)), n_draws), , drop = FALSE]
  }
  
  # Check the scalar parameters once, then map the subject-level z columns below.
  required_scalar_cols <- c("lrn_fr_mu", "lrn_fr_sigma", "dcy_fr_mu", "dcy_fr_sigma")
  missing_scalar_cols <- setdiff(required_scalar_cols, colnames(draw_mat))
  if (length(missing_scalar_cols) > 0) {
    stop("The final_ls_m_val draws object is missing: ", paste(missing_scalar_cols, collapse = ", "))
  }
  
  # Use matrixStats when available; otherwise fall back to base apply().
  col_medians <- function(x) {
    if (requireNamespace("matrixStats", quietly = TRUE)) {
      matrixStats::colMedians(x)
    } else {
      apply(x, 2, median)
    }
  }
  
  subject_summaries <- vector("list", length(sub_ids))
  for (sub_ix in seq_along(sub_ids)) {
    sub_id <- sub_ids[sub_ix]
    sub_design <- trial_template %>%
      filter(sub_index == sub_id) %>%
      arrange(overall_trial_nl)
    
    # Transform this subject's learning and decay parameters for every posterior draw.
    lrn_z_col <- s3_stan_vector_col(colnames(draw_mat), "lrn_fr_z", sub_id)
    dcy_z_col <- s3_stan_vector_col(colnames(draw_mat), "dcy_fr_z", sub_id)
    lrn_fr_draws <- plogis(draw_mat[, "lrn_fr_mu"] + draw_mat[, "lrn_fr_sigma"] * draw_mat[, lrn_z_col])
    dcy_fr_draws <- plogis(draw_mat[, "dcy_fr_mu"] + draw_mat[, "dcy_fr_sigma"] * draw_mat[, dcy_z_col])
    
    # Store only this subject's draw-by-trial matrices, then immediately collapse them.
    q_draws <- matrix(NA_real_, nrow = nrow(draw_mat), ncol = nrow(sub_design))
    m_draws <- matrix(NA_real_, nrow = nrow(draw_mat), ncol = nrow(sub_design))
    for (draw_ix in seq_len(nrow(draw_mat))) {
      draw_diffs <- s3_subject_qm_diff_for_draw(
        sub_design = sub_design,
        lrn_fr = lrn_fr_draws[draw_ix],
        dcy_fr = dcy_fr_draws[draw_ix],
        n_f = n_f
      )
      q_draws[draw_ix, ] <- draw_diffs$q_diff
      m_draws[draw_ix, ] <- draw_diffs$m_diff
    }
    
    subject_summaries[[sub_ix]] <- data.frame(
      sub_index = sub_id,
      overall_trial_nl = sub_design$overall_trial_nl,
      q_diff_median = col_medians(q_draws),
      m_diff_median = col_medians(m_draws)
    )
  }
  
  bind_rows(subject_summaries)
}

# Bin the continuous posterior-median Q/M differences so the manuscript plot can show
# stable choice-probability curves rather than one point per nearly unique x value.
s3_bin_mval_qm_predictors <- function(qm_predictors, n_bins = 9) {
  qm_predictors %>%
    pivot_longer(
      cols = c(q_diff_median, m_diff_median),
      names_to = "predictor",
      values_to = "raw_x"
    ) %>%
    mutate(
      predictor = recode(
        predictor,
        q_diff_median = "Q value",
        m_diff_median = "M value"
      )
    ) %>%
    group_by(predictor) %>%
    mutate(x_value = as.character(ntile(raw_x, n_bins))) %>%
    ungroup() %>%
    group_by(predictor, x_value) %>%
    mutate(x_numeric = median(raw_x, na.rm = TRUE)) %>%
    ungroup() %>%
    select(sub_index, overall_trial_nl, predictor, x_value, x_numeric)
}

# Reuse an already-read final_ls_m_val draws object whenever possible.
if (!exists("s3_amp_mval_learning_draws")) {
  if (exists("final_ls_m_val_learning_draws")) {
    s3_amp_mval_learning_draws <- final_ls_m_val_learning_draws
  } else if (exists("final_ls_m_val_draws")) {
    s3_amp_mval_learning_draws <- final_ls_m_val_draws
  } else {
    s3_amp_mval_learning_draws <- get_draws(
      model = "final_ls_m_val",
      model_out_dir = model_out_dir,
      vars = c("lrn_fr_mu", "lrn_fr_sigma", "lrn_fr_z", "dcy_fr_mu", "dcy_fr_sigma", "dcy_fr_z")
    )
  }
}

# Build and bin the posterior-median Q/M x-axis values once per workspace session.
s3_amp_qm_n_bins <- 5
s3_amp_qm_n_draws <- NULL
if (!exists("s3_amp_mval_qm_predictors")) {
  s3_amp_mval_qm_predictors <- s3_build_mval_qm_predictors(
    trial_template = s3_amp_template,
    mval_learning_draws = s3_amp_mval_learning_draws,
    n_draws = s3_amp_qm_n_draws,
    seed = s3_amp_seed
  )
}
if (!exists("s3_amp_mval_qm_predictor_bins")) {
  s3_amp_mval_qm_predictor_bins <- s3_bin_mval_qm_predictors(
    qm_predictors = s3_amp_mval_qm_predictors,
    n_bins = s3_amp_qm_n_bins
  )
}
if (!exists("s3_amp_observed_qm_choice")) {
  s3_amp_observed_qm_choice <- s3_observed_trial_predictor_choice_summary(
    trial_template = s3_amp_template,
    trial_predictor_bins = s3_amp_mval_qm_predictor_bins
  )
}

# Run the full and A_fr-amputated closed-loop simulations.
set.seed(s3_amp_seed)
s3_amp_closed_summary_set <- s3_run_closed_loop_amputation_summary_set(
  trial_template = s3_amp_template,
  subject_params = s3_amp_params,
  trial_predictor_bins = s3_amp_mval_qm_predictor_bins
)

# Summarize realized stay probabilities and policy-implied p(stay).
s3_amp_closed_sim_draw_summary <- s3_amp_closed_summary_set$sim_draw_summary
s3_amp_closed_sim_summary <- s3_simulated_interval_summary(s3_amp_closed_sim_draw_summary)
s3_amp_closed_plot_summary <- bind_rows(s3_amp_observed_summary, s3_amp_closed_sim_summary)

s3_amp_closed_pred_draw_summary <- s3_amp_closed_summary_set$pred_draw_summary
s3_amp_closed_pred_summary <- s3_simulated_interval_summary(s3_amp_closed_pred_draw_summary)
s3_amp_closed_pred_plot_summary <- bind_rows(s3_amp_observed_summary, s3_amp_closed_pred_summary)

# Summarize left-cue choices by raw last-experience cue-outcome and box-amount histories.
s3_amp_closed_choice_sim_draw_summary <- s3_amp_closed_summary_set$choice_sim_draw_summary
s3_amp_closed_choice_sim_summary <- s3_choice_interval_summary(s3_amp_closed_choice_sim_draw_summary)
s3_amp_closed_choice_sim_plot_summary <- bind_rows(
  s3_amp_observed_last_experience_choice,
  s3_amp_closed_choice_sim_summary
)

# Build the less noisy probability-scale version from the same closed-loop histories.
s3_amp_closed_choice_pred_draw_summary <- s3_amp_closed_summary_set$choice_pred_draw_summary
s3_amp_closed_choice_pred_summary <- s3_choice_interval_summary(s3_amp_closed_choice_pred_draw_summary)
s3_amp_closed_choice_pred_plot_summary <- bind_rows(
  s3_amp_observed_last_experience_choice,
  s3_amp_closed_choice_pred_summary
)

# Summarize the same closed-loop choices by posterior-median Q and M value differences.
s3_amp_closed_qm_choice_sim_draw_summary <- s3_amp_closed_summary_set$trial_predictor_choice_sim_draw_summary
s3_amp_closed_qm_choice_sim_summary <- s3_choice_interval_summary(s3_amp_closed_qm_choice_sim_draw_summary)
s3_amp_closed_qm_choice_sim_plot_summary <- bind_rows(
  s3_amp_observed_qm_choice,
  s3_amp_closed_qm_choice_sim_summary
)

# Build the less noisy probability-scale version for the Q/M x-axis plot.
s3_amp_closed_qm_choice_pred_draw_summary <- s3_amp_closed_summary_set$trial_predictor_choice_pred_draw_summary
s3_amp_closed_qm_choice_pred_summary <- s3_choice_interval_summary(s3_amp_closed_qm_choice_pred_draw_summary)
s3_amp_closed_qm_choice_pred_plot_summary <- bind_rows(
  s3_amp_observed_qm_choice,
  s3_amp_closed_qm_choice_pred_summary
)

# Check closed-loop baseline stay calibration.
s3_amp_closed_overall_draw_summary <- s3_amp_closed_summary_set$overall_draw_summary
s3_amp_closed_overall_summary <- s3_overall_interval_summary(s3_amp_closed_overall_draw_summary)
s3_amp_closed_overall_calibration <- bind_rows(s3_amp_observed_overall, s3_amp_closed_overall_summary)
s3_amp_closed_overall_calibration

# Save closed-loop outputs separately from replay outputs.
s3_amp_closed_prefix <- paste0(s3_amp_dir, "s3_af_amputation_closed_loop_", s3_amp_n_draws, "draws_", s3_amp_timestamp)
write.csv(s3_amp_closed_sim_draw_summary, paste0(s3_amp_closed_prefix, "_sim_draw_summary.csv"), row.names = FALSE)
write.csv(s3_amp_closed_sim_summary, paste0(s3_amp_closed_prefix, "_sim_interval_summary.csv"), row.names = FALSE)
write.csv(s3_amp_closed_pred_draw_summary, paste0(s3_amp_closed_prefix, "_pred_draw_summary.csv"), row.names = FALSE)
write.csv(s3_amp_closed_pred_summary, paste0(s3_amp_closed_prefix, "_pred_interval_summary.csv"), row.names = FALSE)
write.csv(s3_amp_observed_last_experience_choice, paste0(s3_amp_closed_prefix, "_observed_last_experience_choice_summary.csv"), row.names = FALSE)
write.csv(s3_amp_closed_choice_sim_draw_summary, paste0(s3_amp_closed_prefix, "_last_experience_choice_sim_draw_summary.csv"), row.names = FALSE)
write.csv(s3_amp_closed_choice_sim_summary, paste0(s3_amp_closed_prefix, "_last_experience_choice_sim_interval_summary.csv"), row.names = FALSE)
write.csv(s3_amp_closed_choice_pred_draw_summary, paste0(s3_amp_closed_prefix, "_last_experience_choice_pred_draw_summary.csv"), row.names = FALSE)
write.csv(s3_amp_closed_choice_pred_summary, paste0(s3_amp_closed_prefix, "_last_experience_choice_pred_interval_summary.csv"), row.names = FALSE)
write.csv(s3_amp_mval_qm_predictors, paste0(s3_amp_closed_prefix, "_mval_qm_posterior_median_predictors.csv"), row.names = FALSE)
write.csv(s3_amp_mval_qm_predictor_bins, paste0(s3_amp_closed_prefix, "_mval_qm_predictor_bins.csv"), row.names = FALSE)
write.csv(s3_amp_observed_qm_choice, paste0(s3_amp_closed_prefix, "_observed_mval_qm_choice_summary.csv"), row.names = FALSE)
write.csv(s3_amp_closed_qm_choice_sim_draw_summary, paste0(s3_amp_closed_prefix, "_mval_qm_choice_sim_draw_summary.csv"), row.names = FALSE)
write.csv(s3_amp_closed_qm_choice_sim_summary, paste0(s3_amp_closed_prefix, "_mval_qm_choice_sim_interval_summary.csv"), row.names = FALSE)
write.csv(s3_amp_closed_qm_choice_pred_draw_summary, paste0(s3_amp_closed_prefix, "_mval_qm_choice_pred_draw_summary.csv"), row.names = FALSE)
write.csv(s3_amp_closed_qm_choice_pred_summary, paste0(s3_amp_closed_prefix, "_mval_qm_choice_pred_interval_summary.csv"), row.names = FALSE)
write.csv(s3_amp_closed_overall_calibration, paste0(s3_amp_closed_prefix, "_overall_calibration.csv"), row.names = FALSE)
saveRDS(
  list(
    n_draws = s3_amp_n_draws,
    seed = s3_amp_seed,
    sim_draw_summary = s3_amp_closed_sim_draw_summary,
    sim_summary = s3_amp_closed_sim_summary,
    pred_draw_summary = s3_amp_closed_pred_draw_summary,
    pred_summary = s3_amp_closed_pred_summary,
    observed_last_experience_choice = s3_amp_observed_last_experience_choice,
    choice_sim_draw_summary = s3_amp_closed_choice_sim_draw_summary,
    choice_sim_summary = s3_amp_closed_choice_sim_summary,
    choice_pred_draw_summary = s3_amp_closed_choice_pred_draw_summary,
    choice_pred_summary = s3_amp_closed_choice_pred_summary,
    mval_qm_predictors = s3_amp_mval_qm_predictors,
    mval_qm_predictor_bins = s3_amp_mval_qm_predictor_bins,
    observed_mval_qm_choice = s3_amp_observed_qm_choice,
    mval_qm_choice_sim_draw_summary = s3_amp_closed_qm_choice_sim_draw_summary,
    mval_qm_choice_sim_summary = s3_amp_closed_qm_choice_sim_summary,
    mval_qm_choice_pred_draw_summary = s3_amp_closed_qm_choice_pred_draw_summary,
    mval_qm_choice_pred_summary = s3_amp_closed_qm_choice_pred_summary,
    overall_calibration = s3_amp_closed_overall_calibration
  ),
  paste0(s3_amp_closed_prefix, "_summary_objects.rds")
)

# Plot closed-loop realized simulated stay rates.
s3_amp_closed_plot <- plot_s3_amputation_stay(
  summary_df = s3_amp_closed_plot_summary,
  p_values = s3_amp_p_values
)
s3_amp_closed_plot
ggsave(paste0(s3_amp_closed_prefix, "_stay_probability_plot.pdf"), s3_amp_closed_plot, width = 6.2, height = 3.3)

# Plot closed-loop policy-implied p(stay).
s3_amp_closed_pred_plot <- plot_s3_amputation_stay(
  summary_df = s3_amp_closed_pred_plot_summary,
  p_values = s3_amp_p_values
)
s3_amp_closed_pred_plot
ggsave(paste0(s3_amp_closed_prefix, "_predicted_stay_probability_plot.pdf"), s3_amp_closed_pred_plot, width = 6.2, height = 3.3)

# Plot closed-loop realized choices by last cue-outcome and box-amount history.
s3_amp_closed_choice_sim_plot <- plot_s3_amputation_last_experience_choice(
  summary_df = s3_amp_closed_choice_sim_plot_summary
)
s3_amp_closed_choice_sim_plot
ggsave(paste0(s3_amp_closed_prefix, "_last_experience_choice_probability_plot.pdf"), s3_amp_closed_choice_sim_plot, width = 6.2, height = 3.3)

# Plot closed-loop policy-implied p(choose left cue) by the same raw histories.
s3_amp_closed_choice_pred_plot <- plot_s3_amputation_last_experience_choice(
  summary_df = s3_amp_closed_choice_pred_plot_summary
)
s3_amp_closed_choice_pred_plot
ggsave(paste0(s3_amp_closed_prefix, "_last_experience_predicted_choice_probability_plot.pdf"), s3_amp_closed_choice_pred_plot, width = 6.2, height = 3.3)

# Plot closed-loop realized choices by posterior-median Q and M value differences.
s3_amp_closed_qm_choice_sim_plot <- plot_s3_amputation_last_experience_choice(
  summary_df = s3_amp_closed_qm_choice_sim_plot_summary,
  predictor_levels = c("Q value", "M value"),
  x_label = "Posterior-median value difference (left cue - right cue)"
)
s3_amp_closed_qm_choice_sim_plot
ggsave(paste0(s3_amp_closed_prefix, "_mval_qm_choice_probability_plot.pdf"), s3_amp_closed_qm_choice_sim_plot, width = 6.2, height = 3.3)

# Plot closed-loop policy-implied p(choose left cue) by the same Q/M value differences.
s3_amp_closed_qm_choice_pred_plot <- plot_s3_amputation_last_experience_choice(
  summary_df = s3_amp_closed_qm_choice_pred_plot_summary,
  predictor_levels = c("Q value", "M value"),
  x_label = "Posterior-median value difference (left cue - right cue)"
)
s3_amp_closed_qm_choice_pred_plot
ggsave(paste0(s3_amp_closed_prefix, "_mval_qm_predicted_choice_probability_plot.pdf"), s3_amp_closed_qm_choice_pred_plot, width = 6.2, height = 3.3)
```


#Utility vs. reinforcement test

Finally, testing the hypothesis that valence reflects utility rather than reinforcement in this task.

final_ls but affect is reinforcement rather than utility
```{r}
flt_pe <- fit_stan_model(stan_file=paste0(stan_model_dir,"flt_pe.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   n_t = 144)
```

```{r}
flt <- read_fsml("final_ls_test",model_out_dir=model_out_dir)
```

```{r}
flt_pe$loo
```

```{r}
fsml_compare(flt_pe,flt)
```
No real difference here

Now doing the comparison if you only predict choice with modeled affect.
```{r}
mod_aff <- fit_stan_model(stan_file=paste0(stan_model_dir,"mod_aff.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   n_t = 144)
```

```{r}
mod_aff_pe <- fit_stan_model(stan_file=paste0(stan_model_dir,"mod_aff_pe.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   n_t = 144)
```

```{r}
fsml_compare(mod_aff,mod_aff_pe)
```
Still no meaningful difference.


Now, testing if BV impacts choice more as utility or reinforcement
```{r}
rew_bv <- fit_stan_model(stan_file=paste0(stan_model_dir,"rew_bv.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   n_t = 144)
```

```{r}
rew_bv_pe <- fit_stan_model(stan_file=paste0(stan_model_dir,"rew_bv_pe.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   n_t = 144)
```

```{r}
fsml_compare(rew_bv,rew_bv_pe)
```

```{r}
view(filt_sum(rew_bv_pe$sum,"mu"))
```
No difference here either


Now doing the same thing but with r-BV instead of just BV
```{r}
rew_min_bv <- fit_stan_model(stan_file=paste0(stan_model_dir,"rew_min_bv.stan"),
                             model_out_dir=model_out_dir,
                             raw_data=trials,
                             study = "arlbv",
                             chains = 3,
                             n_t = 144)
```

```{r}
rew_min_bv_pe <- fit_stan_model(stan_file=paste0(stan_model_dir,"rew_min_bv_pe.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   chains = 3,
                                   n_t = 144)
```

```{r}
fsml_compare(rew_min_bv,rew_min_bv_pe)
```
Still no difference.

Finally, run these tests with raw valence ratings.
```{r}
two_q_sidebias_pe <- fit_stan_model(stan_file=paste0(stan_model_dir,"two_q_sidebias_pe.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   chains = 4,
                                   n_t = 144)
```

```{r}
fsml_compare(two_q_sidebias_pe,two_q_sidebias)
```
Okay, so when using raw ratings, the model fits better assuming that valence is utility. Now, re-testing without
Q-learning.

```{r}
two_q_sidebias_pe_aonly <- fit_stan_model(stan_file=paste0(stan_model_dir,"two_q_sidebias_pe_aonly.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   chains = 3,
                                   n_t = 144)
```

```{r}
two_q_sidebias_aonly <- fit_stan_model(stan_file=paste0(stan_model_dir,"two_q_sidebias_aonly.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   chains = 3,
                                   n_t = 144)
```

```{r}
fsml_compare(two_q_sidebias_pe_aonly,two_q_sidebias_aonly)
```
Same result, but more dramatic.


Finally, testing whether the effect of valence on choice can be seen to reflect an exponential decay in raw
regression coefficients.

```{r}
trials_diffs <- do.call(rbind,by(trials,trials$sub_index,sub_past_diffs))

diff_reg_fit_1 <- lmer(stay ~ valrat_z_diff_1 + out_diff_1 + (valrat_z_diff_1 + out_diff_1 | sub_index),trials_diffs)
diff_reg_fit_1 <- lm(stay ~ valrat_z_diff_1 + out_diff_1,trials_diffs)

summary(diff_reg_fit_1)

diff_reg_fit_3 <- lmer(stay ~ valrat_z_diff_1 + out_diff_1 + valrat_z_diff_2 + out_diff_2 + valrat_z_diff_3 + out_diff_3 +
                              (valrat_z_diff_1 + out_diff_1 + valrat_z_diff_2 + out_diff_2 + valrat_z_diff_3 + out_diff_3 | sub_index),trials_diffs)

diff_reg_fit_3 <- lm(stay ~ valrat_z_diff_1 + out_diff_1 + valrat_z_diff_2 + out_diff_2 + valrat_z_diff_3 + out_diff_3,trials_diffs)
summary(diff_reg_fit_3)$coefficients
coef_values <- coefficients[2:4, 1]
```

```{r}
library(car)
linearHypothesis(diff_reg_fit_3,"valrat_z_diff_1 - valrat_z_diff_2 = 0")
linearHypothesis(diff_reg_fit_3,"valrat_z_diff_1 - valrat_z_diff_3 = 0")
```

# Get parameter estimates from final model not reported in the main article
```{r}
# Get info on the posterior distribution for all relevant parameters
unreported_params <- "rew_nf_sens_mu|aff_nf_sens_mu|resid_nf_sens_mu|csens_mu|dcy_fr_mu|dcy_nf_mu|lrn_fr_mu|ls_bias_mu|lrn_nf_mu|lrn_c_mu|B_0_mu|B_rew_nf_mu|B_q_fr_mu|B_q_nf_mu|B_pwqd_fr_mu|B_pwqd_nf_mu|B_auto_mu"
up_tab <- select(filt_sum(mod_resid$sum,unreported_params),variable,median,q5,q95)
up_tab[2,3,4] <- as.numeric(up_tab[2,3,4])

# Replace choice predictors with scaled effects
scd_rew_nf_sens_mu <- get_draws("mod_resid",vars=c("scd_rew_nf_sens_mu"), model_out_dir = model_out_dir)
up_tab[1,2:4] <- t(quantile(scd_rew_nf_sens_mu,c(.50,.05,.95)))
scd_aff_nf_sens_mu <- get_draws("mod_resid",vars=c("scd_aff_nf_sens_mu"), model_out_dir = model_out_dir)
up_tab[2,2:4] <- t(quantile(scd_aff_nf_sens_mu,c(.50,.05,.95)))
scd_resid_nf_sens_mu <- get_draws("mod_resid",vars=c("scd_resid_nf_sens_mu"), model_out_dir = model_out_dir)
up_tab[3,2:4] <- t(quantile(scd_resid_nf_sens_mu,c(.50,.05,.95)))
scd_csens_mu <- get_draws("mod_resid",vars=c("scd_csens_mu"), model_out_dir = model_out_dir)
up_tab[5,2:4] <- t(quantile(scd_csens_mu,c(.50,.05,.95)))

up_tab[6:10,2:4] <- sigmoid(up_tab[6:10,2:4]) # Transform learning/decay rates to their original scales

up_tab[,c("median","q5","q95")] <- round(up_tab[,c("median","q5","q95")],2)
write.csv(up_tab,paste0(fig_dir,"unrep_params_s3.csv")) # This CSV will be converted into a figure
```

# Vector-based analysis of choice
```{r}
rew_bv_final <- fit_stan_model(stan_file=paste0(stan_model_dir,"rew_bv_final.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   n_t = 144,
                                   skip=c("check_csvs","loo"))
```


Generate length estimates
```{r}
rb_draws <- get_draws("rew_bv_final",vars=c("rew_fr_sens_mu","bv_fr_sens_mu","B_rew_fr_mu","B_bv_fr_mu"))
vec_ws <- apply(rb_draws,c(1,2), rew_bv_vec_optim) # Estimate vec lengths
vec_ws_org <- aperm(vec_ws, c(2,3,1)) # Get the dimensions back in order

#Get the Manhattan norm ratios for these lengths 
mn_data <- apply(rb_draws[,,c(1:2)],c(1,2),function(x) sum(abs(x))) # Get Manhattan norms
comb_array <- abind(vec_ws_org,mn_data,along=3) 
vec_ws_norm <- apply(comb_array,c(1,2), get_ports) 

#Arrange and name properly
vec_ws_norm_org <- aperm(vec_ws_norm,c(2,3,1)) 
dimnames(vec_ws_norm_org)[[3]] <- c("rew","aff","resid") 
```

Get 95% credible intervals and pd values for all vectors
```{r}
cat("rew\n")
quantile(vec_ws_norm_org[,,"rew"],c(.50,.025,.975))
cat(paste0("pd:", round(mean(vec_ws_norm_org[,,"rew"] > 0) * 100,1)))

cat("\n\naff\n")
quantile(vec_ws_norm_org[,,"aff"],c(.50,.025,.975))
cat(paste0("pd:", round(mean(vec_ws_norm_org[,,"aff"] > 0) * 100,1)))
```

Create interval plots for Manhattan norm ratios
```{r}
variable_intervals<- create_interval_plot(arr = vec_ws_norm_org,names = c("resid","aff","rew"),
                                          xmin = -.012,xmax = 1) +
                        theme(panel.grid.major.x = element_line(color = "#DCDCDC", size = .47),
                              panel.background = element_rect(fill = "white", color = NA),
                              axis.text.x = element_blank(),
                              axis.text.y=element_blank())

#ggsave(paste0(fig_dir,"vec_lens_s3.pdf"),variable_intervals,width=1.8,height=1.35)
```

# Verifying that reward associations have a positive effect on choice
Here, we consider whether the observed effect of reward associations on choice could be due to noise in our
estimates of affect.

First, we fit a model and simulate data in which only affect associations influence choice
```{r}
# aff_only_s3 <- fit_stan_model(stan_file=paste0(stan_model_dir,"aff_only_s3.stan"),
#                                    model_out_dir=model_out_dir,
#                                    raw_data=trials,
#                                    study = "arlbv",
#                                    n_t = 144,
#                                    skip=c("check_csvs","loo"))
aff_only_s3 <- read_fsml("aff_only_s3",model_out_dir=model_out_dir)
```

For each simulated dataset, we estimate the effects of Q and A on choice, using an analysis method that 
efficiently approximates the model reported in the manuscript
```{r}
# Get necessary data
trials_bqba_sim <- trials %>% select(sub_index,block,overall_trial_nl,fA_ix,fB_ix,rat_number,show_fres,out,box_val)

# Add parameter means needed for approximate data analysis
trials_bqba_sim <- add_param_means(aff_only_s3$sum,"lrn_fr",trials_bqba_sim)
trials_bqba_sim <- add_param_means(aff_only_s3$sum,"lrn_nf",trials_bqba_sim)
trials_bqba_sim <- add_param_means(aff_only_s3$sum,"dcy_fr",trials_bqba_sim)
trials_bqba_sim <- add_param_means(aff_only_s3$sum,"dcy_nf",trials_bqba_sim)
trials_bqba_sim <- add_param_means(aff_only_s3$sum,"lrn_c",trials_bqba_sim)

# Get simulated data
sim_choice <- get_draws(model="aff_only_s3",vars=c("sim_choice"),model_out_dir=model_out_dir)
sim_rat <- get_draws("aff_only_s3",vars=c("sim_rat"),model_out_dir=model_out_dir)
sim_prat <- get_draws("aff_only_s3",vars=c("sim_prat"),model_out_dir=model_out_dir)

plan(multisession, workers = 12)
registerDoFuture()

sim_effs <- data.frame("bQs"=c(),"bAs"=c())
for(chunk in 1:8){
  # Divide the simulations into 8 chunks, to avoid overtaxing memory
  iters <- ((chunk-1)*125+1):(chunk*125)
  sim_choice_chunk <- sim_choice[iters,,]
  sim_prat_chunk <- sim_prat[iters,,]
  sim_rat_chunk <- sim_rat[iters,,]
  chunk_effs <- foreach(i = 1:125, .combine = rbind) %dopar% {
    iter_effs <- data.frame(matrix(0,ncol=2,nrow=4))
    colnames(iter_effs) <- c("bQs","bAs")
    for(c in 1:4){
      # Add simulated choices and ratings to the data
      sim_trials <- trials_bqba_sim %>% 
                      mutate(choice=as.vector(sim_choice_chunk[i,c,])) %>%
                      mutate(prat=as.vector(sim_prat_chunk[i,c,])) %>%
                      left_join(data.frame(valrat_z = as.vector(sim_rat_chunk[i,c,]),rat_number = 1:dim(sim_rat_chunk)[3]),
                                by="rat_number") %>%
                      mutate(chosen_frac = ifelse(choice == 1,fA_ix,fB_ix)) %>%
                      mutate(unchosen_frac = ifelse(choice == 1,fB_ix,fA_ix))
      # Get estimated effects of Q and A on choice
      est_eff <- est_bq_ba_s3(sim_trials)
      iter_effs$bQs[c] <- est_eff$bQ
      iter_effs$bAs[c] <- est_eff$bA
    }
    return(iter_effs)
  }
  sim_effs <- rbind(sim_effs,chunk_effs)
}
save(sim_effs,file=paste0(path_to_project_directory,"output/s3_aff_only_sim_effs.Rdata"))
```

Next, we run these same approximate analyses on the real data
```{r}
# Get necessary data
trials_bqba_real <- trials %>% select(sub_index,block,overall_trial_nl,fA_ix,fB_ix,rat_number,show_fres,
                                      out,box_val,choice_numeric,valrat_z,prev_rate,chosen_frac,unchosen_frac) %>%
                               rename(prat = prev_rate, choice = choice_numeric)

final_ls <- read_fsml("final_ls",model_out_dir=model_out_dir)
# Add parameter means needed for approximate data analysis
trials_bqba_real <- add_param_means(final_ls$sum,"lrn_fr",trials_bqba_real)
trials_bqba_real <- add_param_means(final_ls$sum,"lrn_nf",trials_bqba_real)
trials_bqba_real <- add_param_means(final_ls$sum,"dcy_fr",trials_bqba_real)
trials_bqba_real <- add_param_means(final_ls$sum,"dcy_nf",trials_bqba_real)
trials_bqba_real <- add_param_means(final_ls$sum,"lrn_c",trials_bqba_real)

real_effs <- est_bq_ba_s3(trials_bqba_real)
save(real_effs,file=paste0(path_to_project_directory,"output/s3_aff_only_real_effs.Rdata"))
```

Finally, we plot the simulated and actual effects for comparison
```{r}
bq_sims <- ggplot(sim_effs, aes(x = bQs)) +
            geom_histogram(fill = "steelblue", color = "black") +  # Adjust binwidth as needed
            geom_vline(xintercept = 0, color = "black", size = 1) +  # Black vertical line at 0
            geom_vline(xintercept = real_effs$bQ, color = "red", size = 1) +
            theme_minimal() +
            theme(
              panel.grid.major.y = element_blank(),  # Remove major vertical grid lines
              panel.grid.minor.y = element_blank(),      
              panel.grid.major.x = element_blank(),  # Remove major vertical grid lines
              panel.grid.minor.x = element_blank(), 
              axis.title.x = element_blank(),       # Remove x-axis label
              axis.title.y = element_blank(),        # Remove y-axis label
              axis.ticks.y = element_blank(),
              axis.text.y = element_blank()
            )
ggsave("/Users/dp/Documents/manuscripts/vrv/figures_tables/supp_fig_2a_s3.pdf",bq_sims,width=2,height=1.33)
```

```{r}
ba_sims <- ggplot(sim_effs, aes(x = bAs)) +
            geom_histogram(fill = "steelblue", color = "black") +  # Adjust binwidth as needed
            geom_vline(xintercept = 0, color = "black", linewidth = 1) +  # Black vertical line at 0
            geom_vline(xintercept = real_effs$bA, color = "red", linewidth = 1) +
                      theme_minimal() +
                      theme(
                        panel.grid.major.y = element_blank(),  # Remove major vertical grid lines
                        panel.grid.minor.y = element_blank(),      
                        panel.grid.major.x = element_blank(),  # Remove major vertical grid lines
                        panel.grid.minor.x = element_blank(), 
                        axis.title.x = element_blank(),       # Remove x-axis label
                        axis.title.y = element_blank(),        # Remove y-axis label
                        axis.ticks.y = element_blank(),
                        axis.text.y = element_blank())
ggsave("/Users/dp/Documents/manuscripts/vrv/figures_tables/supp_fig_2b_s3.pdf",ba_sims,width=2,height=1.33)
```


# Fitting model with just q-learning

```{r}
q_only <- fit_stan_model(stan_file=paste0(stan_model_dir,"q_only.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   n_t = 144,
                                   skip=c("check_csvs","loo"))
```

```{r}
scd_rew_fr_sens_mu_q_only <- get_draws("q_only",model_out_dir=model_out_dir,vars=c("scd_rew_fr_sens_mu"))
get_ci_pd(draws = scd_rew_fr_sens_mu_q_only)
```

```{r}
lrn_fr_mu_q_only <- get_draws("q_only",model_out_dir=model_out_dir,vars=c("lrn_fr_mu"))
get_ci_pd(draws = sigmoid(lrn_fr_mu_q_only))
```

# Compare learning rates across studies
Study 3 learning rate
```{r}
lrn_s3 <- sigmoid(get_draws("final_ls",vars=c("lrn_fr_mu")))
lrn_s2 <- sigmoid(get_draws("model_pred_arl_nonuis",vars=c("alpha_mu"),model_out_dir="/Users/dp/projects/s22_follow_up/output/results/stan_model_fits/"))
lrn_s1 <- sigmoid(get_draws("arl",vars=c("alpha_mu"),model_out_dir="~/projects/spring_2022_study/output/results/stan_model_fits/final_models/"))
quantile(lrn_s3,c(.025,.50,.975))
get_ci_pd(draws=lrn_s3[1:1500,,]-lrn_s2) # pare down the lrn_s3 posterior to make it comparable to the lrn_s2 and lrn_s1 posteriors
get_ci_pd(draws=lrn_s3[1:1500,,]-lrn_s1)
```



# Outputting bq(Q_a-Q_b) + bq(A_a-A_b)
Refit the main model, outputting bq(Q_a-Q_b) + ba(A_a-A_b) for each trial
```{r}
arlbv_qa_term_out <- fit_stan_model(stan_file=paste0(stan_model_dir,"arlbv_qa_term_out.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   n_t = 144)
```


```{r}
q_a_term_draws <- get_draws("arlbv_qa_term_out",vars=c("q_a_term"))
q_a_term_abs <- q_a_term_draws^2
s_s3 <- apply(q_a_term_abs,c(1,2),mean)
quantile(s_s3,c(.025,.50,.975))
```

Now compare this to the same variable for studies 1 and 2
```{r}
q_a_term_draws_s1 <- get_draws("arl_qa_term_out",vars=c("q_a_term"), model_out_dir = "~/projects/spring_2022_study/output/results/stan_model_fits/final_models/")
q_a_term_abs_s1 <- q_a_term_draws_s1^2
s_s1 <- apply(q_a_term_abs_s1,c(1,2),mean)
quantile(s_s1,c(.025,.50,.975))
get_ci_pd(draws=s_s3-s_s1)
```

```{r}
q_a_term_draws_s2 <- get_draws("s22fu_qa_term_out",vars=c("q_a_term"),model_out_dir="/Users/dp/projects/s22_follow_up/output/results/stan_model_fits/")
q_a_term_abs_s2 <- q_a_term_draws_s2^3
s_s2 <- apply(q_a_term_abs_s2,c(1,2),mean)
quantile(s_s2,c(.025,.50,.975))
get_ci_pd(draws=s_s3-s_s2)
```

# Calculating correlations between reward and box values, valence rating residuals
```{r}
rat_pred <- get_draws("final_ls",model_out_dir=model_out_dir,vars=("rat_pred"))
trials_rat <- filter(trials,!is.na(val_rat))
fres_trials <- which(trials_rat$show_fres == 1)
fres_rat_pred <- rat_pred[,,fres_trials]
trials_rat_fres <- filter(trials_rat,show_fres == 1)
res_rew_cor <- apply(fres_rat_pred,c(1,2),function(x) cor(trials_rat_fres$valrat_z-x,trials_rat_fres$out))
get_ci_pd(draws = res_rew_cor,round = 100)
```

# Assessing effect of box value associations on choice
```{r}
final_ls_m_val <- fit_stan_model(stan_file=paste0(stan_model_dir,"final_ls_m_val.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   n_t = 144,
                                   iter_sampling = 2000,
                                   skip=c("check_csvs","loo"))
```

```{r}
final_ls_m_val$diagnostics
beta_m <- get_draws("final_ls_m_val",vars=c("scd_box_fr_sens_mu"),model_out_dir=model_out_dir)
get_ci_pd(draws=beta_m)
```

# No-autocorrelation model variant

Fit no-choice-autocorrelation version of the main choice model.
```{r}
final_ls_nocac <- fit_stan_model(stan_file=paste0(stan_model_dir,"final_ls_nocac.stan"),
                                   model_out_dir=model_out_dir,
                                   raw_data=trials,
                                   study = "arlbv",
                                   n_t = 144)
```

Assess effects of Q and A on choice from the no-autocorrelation posterior.
```{r}
scd_rew_fr_sens_mu_nocac <- get_draws("final_ls_nocac",vars=c("scd_rew_fr_sens_mu"),model_out_dir=model_out_dir)
scd_aff_fr_sens_mu_nocac <- get_draws("final_ls_nocac",vars=c("scd_aff_fr_sens_mu"),model_out_dir=model_out_dir)
scd_aff_fr_sens_mu_nocac <- get_draws("final_ls_nocac",vars=c("scd_resid_fr_sens_mu_nocac"),model_out_dir=model_out_dir)

get_ci_pd(draws = scd_rew_fr_sens_mu_nocac)
get_ci_pd(draws = scd_aff_fr_sens_mu_nocac)
get_ci_pd(draws = scd_aff_fr_sens_mu_nocac - scd_rew_fr_sens_mu_nocac)
```

# Parameter recovery for Study 3 choice effects
Simulate and recover `B_Q` (`rew_fr_sens_mu`), `B_A` (`aff_fr_sens_mu`), and `B_R` (`resid_fr_sens_mu`)
from the fitted Study 3 choice model.
```{r, eval=FALSE}
# Select which fitted model summary to use as the simulation anchor.
choice_model_name <- "final_ls"
choice_model_sum <- read_fsml(choice_model_name, model_out_dir = model_out_dir)$sum

# Run the full Study 3 simulation + recovery pipeline.
s3_choice_recovery <- run_s3_choice_param_recovery(
  trials = trials,
  sum_df = choice_model_sum,
  n_sims = 500,
  seed = 19
)

rec_dir <- paste0(path_to_project_directory, "output/recovery/")
if (!dir.exists(rec_dir)) {
  dir.create(rec_dir, recursive = TRUE)
}

# Create timestamped output filenames to avoid overwriting prior runs.
timestamp <- format(Sys.time(), "%Y%m%d_%H%M%S")
estimates_file <- paste0(rec_dir, "s3_choice_param_recovery_estimates_", timestamp, ".csv")
fail_file <- paste0(rec_dir, "s3_choice_param_recovery_fail_summary_", timestamp, ".csv")
plot_file <- paste0(rec_dir, "s3_choice_param_recovery_panel_", timestamp, ".pdf")

# Save row-level estimates and failure summaries for reproducibility.
write.csv(s3_choice_recovery$estimates, estimates_file, row.names = FALSE)
write.csv(s3_choice_recovery$fail_summary, fail_file, row.names = FALSE)

# Build and save the faceted true-vs-recovered panel.
s3_choice_recovery_plot <- plot_s3_choice_param_recovery(
  estimates_df = s3_choice_recovery$estimates,
  point_alpha = 0.35,
  point_size = 1.35
)
ggsave(plot_file, s3_choice_recovery_plot, width = 5.31, height = 2)

s3_choice_recovery$fail_summary
```

Rebuild the recovery panel directly from a saved estimates CSV.
```{r, eval=FALSE}
# Recreate the panel from a previously saved estimates file (no re-simulation required).
replot_s3 <- build_s3_choice_param_recovery_plot_from_file(
  estimates_file = paste0(rec_dir, "s3_choice_param_recovery_estimates_YYYYMMDD_HHMMSS.csv"),
  point_alpha = 0.35,
  point_size = 1.35
)

ggsave(
  filename = paste0(rec_dir, "s3_choice_param_recovery_panel_replot.pdf"),
  plot = replot_s3$panel_plot,
  width = 5.31,
  height = 2
)
```
